---
title: "Bulk RNA-seq Analysis Report"
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    format-links: false
    embed-resources: true
    code-fold: true
    theme: zephyr
    css: assets/style.css
    include-after-body: assets/report-ui.html
    fig-align: center
    fig-responsive: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: false
    fig-align: center
    pdf-engine: xelatex
    geometry:
      - margin=0.65in
    colorlinks: true
    documentclass: article
    papersize: letter
knitr:
  opts_chunk:
    dev: "png"
    dpi: 110
    fig.retina: 2
    out.width: "100%"
params:
  config_path: "config/config.yaml"
  project_root: "."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)

# Allow reused chunk labels inside per-contrast knit_child loops;
# knitr auto-suffixes so figure files become <label>-1.png, <label>-2.png, ...
options(knitr.duplicate.label = "allow")

suppressPackageStartupMessages({
  library(yaml)
  library(readr)
  library(dplyr)
  library(tidyr)
  library(tibble)
  library(ggplot2)
  library(DT)
  library(plotly)
})

`%||%` <- function(a, b) if (is.null(a)) b else a

project_root <- normalizePath(params$project_root, mustWork = TRUE)
config_path  <- normalizePath(params$config_path,  mustWork = TRUE)

# All downstream paths are resolved relative to the project root.
rp <- function(...) file.path(project_root, ...)

cfg      <- yaml::read_yaml(config_path)
project  <- cfg$project       %||% list()
exp_meta <- project$experiment %||% list()

samples_tsv   <- rp(cfg$input$samples_tsv)
contrasts_tsv <- rp(cfg$input$contrasts_tsv)

samples   <- readr::read_tsv(samples_tsv,   show_col_types = FALSE)
contrasts <- readr::read_tsv(contrasts_tsv, show_col_types = FALSE)

# Helper to look up contrast metadata by id.
contrast_row <- function(cid) {
  out <- contrasts[contrasts$contrast_id == cid, , drop = FALSE]
  if (nrow(out) == 0) return(NULL)
  as.list(out[1, ])
}

# Shared helper: emit "no results available" card.
no_results <- function(msg = "No results available for this section.") {
  htmltools::div(
    class  = "callout callout-note",
    style  = "padding:0.75em 1em;border-left:4px solid #8aa;background:#f5f7f9;margin:0.5em 0;",
    htmltools::tags$em(msg)
  )
}

# Safe CSV/TSV loader: returns NULL on missing/unreadable/empty.
safe_read <- function(path, sep = ",") {
  if (is.null(path) || !file.exists(path)) return(NULL)
  df <- tryCatch(
    if (sep == "\t") {
      readr::read_tsv(path, show_col_types = FALSE)
    } else {
      readr::read_csv(path, show_col_types = FALSE)
    },
    error = function(e) NULL
  )
  if (is.null(df) || nrow(df) == 0) return(df)  # keep empty DF for header-only files
  df
}

fmt_num <- function(x, digits = 3) {
  if (is.null(x) || length(x) == 0) return(NA_character_)
  formatC(x, format = "g", digits = digits)
}

is_html_report <- function() isTRUE(knitr::is_html_output())

report_table <- function(data, rownames = FALSE, filter = "top",
                         extensions = NULL, options = list(),
                         caption = NULL, signif_cols = character(),
                         digits = 3) {
  data <- as.data.frame(data)
  if (is_html_report()) {
    dt_args <- list(
      data = data,
      rownames = rownames,
      filter = filter,
      caption = caption,
      options = options
    )
    if (!is.null(extensions)) dt_args$extensions <- extensions
    dt <- do.call(DT::datatable, dt_args)
    if (length(signif_cols) > 0) {
      dt <- DT::formatSignif(dt, columns = intersect(signif_cols, names(data)),
                             digits = digits)
    }
    return(dt)
  }

  static <- data
  for (col in intersect(signif_cols, names(static))) {
    if (is.numeric(static[[col]])) static[[col]] <- signif(static[[col]], digits)
  }
  max_rows <- options$pageLength %||% min(25, nrow(static))
  if (is.finite(max_rows) && nrow(static) > max_rows) {
    static <- utils::head(static, max_rows)
    caption <- paste(caption %||% "", sprintf("(showing first %d rows)", max_rows))
  }
  knitr::kable(static, caption = caption, booktabs = TRUE, longtable = TRUE)
}
```

::: {.panel-tabset .hidden}
:::

# Cover

```{r cover, results='asis'}
project_name <- project$name   %||% "Bulk RNA-seq Project"
analyst      <- project$analyst %||% "n/a"
report_date  <- format(Sys.Date(), "%Y-%m-%d")

cell_line <- exp_meta$cell_line %||% ""
compound  <- exp_meta$compound  %||% ""
dose      <- exp_meta$dose      %||% ""
duration  <- exp_meta$duration  %||% ""
notes     <- exp_meta$notes     %||% ""

empty_dash <- function(x) if (is.null(x) || is.na(x) || !nzchar(x)) "ŌĆö" else x

cat("**Project:** ", project_name, "  \n", sep = "")
cat("**Prepared by:** ", analyst,  "  \n", sep = "")
cat("**Report date:** ", report_date, "\n\n", sep = "")

cat("## Experiment\n\n")
cat("| Field | Value |\n|---|---|\n")
cat(sprintf("| Cell line | %s |\n", empty_dash(cell_line)))
cat(sprintf("| Compound  | %s |\n", empty_dash(compound)))
cat(sprintf("| Dose      | %s |\n", empty_dash(dose)))
cat(sprintf("| Duration  | %s |\n", empty_dash(duration)))
cat(sprintf("| Notes     | %s |\n", empty_dash(notes)))
cat("\n")

cat("## Design\n\n")
cat(sprintf("- Samples: **%d**\n", nrow(samples)))
if ("condition" %in% names(samples)) {
  cond_tbl <- sort(table(samples$condition))
  cat("- Condition counts:\n")
  for (nm in names(cond_tbl)) {
    cat(sprintf("  - %s: %d\n", nm, cond_tbl[[nm]]))
  }
}
cat(sprintf("- Contrasts defined: **%d**\n", nrow(contrasts)))
cat("\n")
```

### Samples

```{r cover-samples}
knitr::kable(samples, row.names = FALSE, booktabs = TRUE, longtable = TRUE)
```

### Contrasts

```{r cover-contrasts}
knitr::kable(contrasts, row.names = FALSE, booktabs = TRUE, longtable = TRUE)
```

# Analysis workflow

```{mermaid}
flowchart TD
    A[nf-core/rnaseq ┬Ę salmon counts] --> B[QC summary ┬Ę MultiQC]
    A --> C[Exploratory ┬Ę VST / PCA / sample correlation]
    C --> D[Differential expression ┬Ę DESeq2 + apeglm]
    D --> E[Functional enrichment]
    E --> E1[GSEA ┬Ę MSigDB]
    E --> E2[ORA ┬Ę GO / KEGG / Reactome / Hallmark]
    D --> F[TFEA ┬Ę decoupler ULM + CollecTRI]
    D --> G[Pathway activity ┬Ę PROGENy]
    D --> H[cMap ┬Ę L2S2 / LINCS]
```

## Report structure and interpretation

::: {.lang-en}

| Stage | Analytical objective | Method | Primary deliverable |
|---|---|---|---|
| **Quality control** | Assess library preparation and alignment integrity. | MultiQC aggregation of FastQC, STAR/Salmon, and RSeQC metrics. | Per-sample table of duplication, alignment rate, rRNA contamination, and strandedness. |
| **Exploratory analysis** | Evaluate sample grouping structure and detect outliers prior to inference. | VST-transformed counts; PCA on top 500 most-variable genes; sample-to-sample correlation. | PCA projection, correlation heatmap, dendrogram. |
| **Differential expression** | Quantify condition-associated changes in gene expression. | DESeq2 Wald test with apeglm log-fold-change shrinkage. | Results table with shrunken LFC, Wald statistic, and adjusted *p*-values; volcano, MA, and top-DEG heatmap. |
| **Gene set enrichment (GSEA)** | Identify gene sets coordinately perturbed across the full ranked list. | Pre-ranked GSEA on Wald statistic across selected MSigDB collections. | Normalized enrichment score and adjusted *p*-value per gene set. |
| **Over-representation (ORA)** | Identify pathways enriched among the DEG shortlist. | Hypergeometric test against GO, KEGG, Reactome, and Hallmark databases. | Raw and adjusted *p*-values per pathway and database. |
| **TFEA** | Infer upstream regulators consistent with the observed expression changes. | decoupleR univariate linear model (ULM) applied to the CollecTRI regulon network. | Per-sample TF activity scores with significance. |
| **Pathway activity** | Estimate canonical signalling-pathway activity per sample. | PROGENy with top responsive targets; z-scored activity with treatedŌłÆcontrol delta. | Per-sample pathway activity matrix and contrast-level summary. |
| **cMap** | Identify perturbagens producing transcriptomic signatures concordant or discordant with the contrast. | L2S2 / LINCS L1000 signature query using top up- and down-regulated genes. | Ranked perturbagen table with connectivity scores. |
| **Audit trail** | Ensure reproducibility and provenance of the analysis. | Snapshot of configuration, input checksums, and computational environment. | Resolved config, input MD5 sums, and full session information. |
:::

::: {.lang-ko}

| ļŗ©Ļ│ä | ļČäņäØ ļ¬®ņĀü | ļ░®ļ▓Ģ | ņŻ╝ ņé░ņČ£ļ¼╝ |
|---|---|---|---|
| **Quality control** | ļØ╝ņØ┤ļĖīļ¤¼ļ”¼ ņżĆļ╣äņÖĆ ņĀĢļĀ¼ ĒÆłņ¦ł ĒÅēĻ░Ć. | FastQC, STAR/Salmon, RSeQC metricņØä MultiQCļĪ£ ņ¦æĻ│ä. | ņāśĒöīļ│ä duplication, alignment rate, rRNA contamination, strandedness. |
| **ĒāÉņāē ļČäņäØ** | ņāśĒöī ĻĘĖļŻ╣ ĻĄ¼ņĪ░ ĒÖĢņØĖ ļ░Å Outlier ĒÖĢņØĖ. | VST ļ│ĆĒÖś ņ╣┤ņÜ┤ĒŖĖ ┬Ę top 500 variable gene PCA ┬Ę ņāśĒöī-ņāśĒöī Correlation. | PCA Ēł¼ņśü, ņāüĻ┤Ć heatmap, dendrogram. |
| **ņ░©ļō▒ļ░£Ēśä** | ņĪ░Ļ▒┤ļ│ä ņ£ĀņĀäņ×É ļ░£Ēśä ļ│ĆĒÖö ņĀĢļ¤ēĒÖö. | DESeq2 Wald test + apeglm log-fold-change shrinkage. | shrunken LFC, Wald statistic, ņĪ░ņĀĢ *p*-value Ļ▓░Ļ│╝ Ēæ£ ┬Ę volcano ┬Ę MA ┬Ę top-DEG heatmap. |
| **Gene set enrichment (GSEA)** | ĒÖ£ņä▒/ļ╣äĒÖ£ņä▒ĒÖö ļÉ£ gene set ĒāÉņāē. | ņäĀĒāØļÉ£ MSigDB collectionņŚÉ ļīĆĒĢ┤ Wald statistic ĻĖ░ļ░ś pre-ranked GSEA. | Gene setļ│ä NES ļ░Å ņĪ░ņĀĢ *p*-value. |
| **Over-representation (ORA)** | DEG ļ¬®ļĪØņŚÉņä£ Ļ│╝ļīĆĒæ£ĒśäļÉ£ pathway ĒÖĢņØĖ. | GO, KEGG, Reactome, Hallmark DBņŚÉ ļīĆĒĢ£ hypergeometric test. | Pathway┬ĘDBļ│ä raw / adjusted *p*-value. |
| **TFEA** | ļ░£Ēśä Ēī©Ēä┤ņØä ņäżļ¬ģĒĢśļŖö ņāüņ£ä ņĪ░ņĀłņ×É ņČöļĪĀ. | CollecTRI regulon ļäżĒŖĖņøīĒü¼ņŚÉ ļīĆĒĢ£ decoupleR ULM. | ņāśĒöīļ│ä TF ĒÖ£ņä▒ scoreņÖĆ ņ£ĀņØśņä▒. |
| **Pathway ĒÖ£ņä▒ļÅä** | ņāśĒöīļ│ä canonical signalling pathway ĒÖ£ņä▒ ņČöņĀĢ. | PROGENy (top responsive targets) ┬Ę z-scored ĒÖ£ņä▒ļÅä ┬Ę treatedŌłÆcontrol delta. | ņāśĒöīļ│ä pathway ĒÖ£ņä▒ļÅä Ē¢ēļĀ¼, contrast ņłśņżĆ ņÜöņĢĮ. |
| **cMap** | ĒĢ┤ļŗ╣ contrastņÖĆ ņØ╝ņ╣śĒĢśĻ▒░ļéś ļ░śļīĆļÉśļŖö transcriptomic signatureņØś perturbagen ĒāÉņāē. | Top up / down ņ£ĀņĀäņ×ÉļĪ£ L2S2 / LINCS L1000 signature ņ¦łņØś. | Connectivity score ĻĖ░ļ░ś perturbagen ranking Ēæ£. |
| **Audit trail** | ļČäņäØ ņ×¼Ēśäņä▒Ļ│╝ provenance ļ│┤ņ×ź. | Config snapshot, ņ×ģļĀź checksum, Ļ│äņé░ ĒÖśĻ▓Į ņŖżļāģņāĘ. | ņĄ£ņóģ config, ņ×ģļĀź MD5, ņäĖņģś ņĀĢļ│┤. |
:::

{{< include sections/_qc.qmd >}}

{{< include sections/_exploratory.qmd >}}

{{< include sections/_de.qmd >}}

{{< include sections/_enrichment.qmd >}}

{{< include sections/_cmap.qmd >}}

# Audit trail

## Input provenance

::: {.lang-en}
- Gene counts: nf-core/rnaseq `salmon.merged.gene_counts_length_scaled.tsv`
- `log2FoldChange` values reported in DE results are **apeglm-shrunken**.
- `stat` values are **unshrunk Wald test statistics** (used as the GSEA ranking metric).
:::

::: {.lang-ko}
- ņ£ĀņĀäņ×É ņ╣┤ņÜ┤ĒŖĖ: nf-core/rnaseq `salmon.merged.gene_counts_length_scaled.tsv`.
- DE Ļ▓░Ļ│╝ņØś `log2FoldChange`ļŖö **apeglmņ£╝ļĪ£ shrinkļÉ£ Ļ░Æ**.
- `stat`ņØĆ **shrinkļÉśņ¦Ć ņĢŖņØĆ Wald test ĒåĄĻ│äļ¤ē** (GSEA ranking metric).
:::

## Cutoffs in use

```{r audit-cutoffs, results='asis'}
de_cfg <- cfg$de %||% list()
prim   <- de_cfg$primary   %||% list(padj = NA, abs_lfc = NA)
sec    <- de_cfg$secondary %||% list(padj = NA, abs_lfc = NA)
ora_cfg <- cfg$enrichment$ora  %||% list()
gsea_cfg <- cfg$enrichment$gsea %||% list()
tf_cfg   <- cfg$tfea    %||% list()
pw_cfg   <- cfg$progeny %||% list()
dr_cfg   <- cfg$cmap    %||% list()

cat("| Setting | Value |\n|---|---|\n")
cat(sprintf("| DE prefilter (min count / mode) | %s / %s |\n",
            de_cfg$prefilter_min_count %||% "ŌĆö",
            de_cfg$prefilter_min_samples_mode %||% "ŌĆö"))
cat(sprintf("| DE LFC shrink | %s |\n", de_cfg$lfc_shrink %||% "ŌĆö"))
cat(sprintf("| Enrichment enabled | %s |\n", cfg$enrichment$enabled %||% "ŌĆö"))
cat(sprintf("| TFEA enabled | %s |\n", cfg$tfea$enabled %||% "ŌĆö"))
cat(sprintf("| PROGENy enabled | %s |\n", cfg$progeny$enabled %||% "ŌĆö"))
cat(sprintf("| cMap enabled | %s |\n", cfg$cmap$enabled %||% "ŌĆö"))
cat(sprintf("| Primary DEG | padj < %s & |LFC| >= %s |\n",
            prim$padj   %||% "ŌĆö", prim$abs_lfc   %||% "ŌĆö"))
cat(sprintf("| Secondary DEG | padj < %s & |LFC| >= %s |\n",
            sec$padj    %||% "ŌĆö", sec$abs_lfc    %||% "ŌĆö"))
cat(sprintf("| ORA min / max input genes | %s / %s |\n",
            ora_cfg$min_input_genes %||% "ŌĆö", ora_cfg$max_input_genes %||% "ŌĆö"))
cat(sprintf("| ORA databases | %s |\n",
            paste(vapply(ora_cfg$databases %||% list(),
                         function(d) d$label %||% d$id, character(1)),
                  collapse = ", ")))
cat(sprintf("| GSEA ranking / min / max / seed | %s / %s / %s / %s |\n",
            gsea_cfg$ranking %||% "ŌĆö",
            gsea_cfg$min_size %||% "ŌĆö",
            gsea_cfg$max_size %||% "ŌĆö",
            gsea_cfg$seed %||% "ŌĆö"))
cat(sprintf("| GSEA collections | %s |\n",
            paste(vapply(gsea_cfg$collections %||% list(),
                         function(c) c$label %||% c$id, character(1)),
                  collapse = ", ")))
cat(sprintf("| TFEA (method / min_size / top_n) | %s / %s / %s |\n",
            tf_cfg$method %||% "ŌĆö",
            tf_cfg$min_size %||% "ŌĆö",
            tf_cfg$top_n %||% "ŌĆö"))
cat(sprintf("| PROGENy top targets | %s |\n", pw_cfg$top_targets %||% "ŌĆö"))
cat(sprintf("| cMap (service / top_up / top_down) | %s / %s / %s |\n",
            dr_cfg$service %||% "ŌĆö",
            dr_cfg$top_up  %||% "ŌĆö",
            dr_cfg$top_down %||% "ŌĆö"))
cat("\n")
```

## Reproducibility summary

```{r audit-reproducibility}
file_meta <- function(label, path) {
  resolved <- if (is.null(path) || is.na(path) || !nzchar(path)) {
    NA_character_
  } else if (grepl("^/", path)) {
    path
  } else {
    file.path(project_root, path)
  }

  exists <- !is.na(resolved) && file.exists(resolved)
  info <- if (exists) file.info(resolved) else NULL
  md5 <- if (exists) unname(tools::md5sum(resolved)) else NA_character_

  data.frame(
    item = label,
    path = if (is.na(resolved)) NA_character_ else normalizePath(resolved, winslash = "/", mustWork = FALSE),
    exists = exists,
    size_bytes = if (exists) info$size else NA_real_,
    modified = if (exists) format(info$mtime, "%Y-%m-%d %H:%M:%S %Z") else NA_character_,
    md5 = md5,
    stringsAsFactors = FALSE
  )
}

# Canonical pipeline version lives in the `VERSION` file at the workflow
# source root. The path is resolved relative to this template so it works
# regardless of project_root: inside Docker the template sits at /app/report/
# and the VERSION file at /app/VERSION; in Colab/native clones the same
# relative layout holds.
.tpl_dir <- tryCatch(dirname(knitr::current_input(dir = TRUE)),
                     error = function(e) NULL)
.version_path <- if (!is.null(.tpl_dir)) file.path(.tpl_dir, "..", "VERSION") else NULL
pipeline_version <- if (!is.null(.version_path) && file.exists(.version_path)) {
  trimws(readLines(.version_path, n = 1, warn = FALSE))
} else "unknown"

run_meta <- data.frame(
  item = c("Report render time", "Pipeline version", "Project root", "Config used by report"),
  value = c(
    format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z"),
    pipeline_version,
    project_root,
    config_path
  ),
  stringsAsFactors = FALSE
)

report_table(
  run_meta,
  rownames = FALSE,
  options = list(pageLength = 4, dom = "t", scrollX = TRUE)
)

input_meta <- dplyr::bind_rows(
  file_meta("Config YAML", config_path),
  file_meta("Counts TSV", cfg$input$counts_tsv %||% NA_character_),
  file_meta("Samples TSV", cfg$input$samples_tsv %||% NA_character_),
  file_meta("Contrasts TSV", cfg$input$contrasts_tsv %||% NA_character_),
  file_meta("MultiQC data directory", cfg$input$multiqc_data_dir %||% NA_character_)
)

report_table(
  input_meta,
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 10,
    lengthMenu = c(10, 25, 50),
    scrollX = TRUE,
    autoWidth = FALSE,
    dom = "lfrtip",
    columnDefs = list(
      list(targets = which(names(input_meta) == "path") - 1,
           className = "pathway-name-column"),
      list(targets = which(names(input_meta) == "md5") - 1,
           className = "pathway-name-column")
    )
  )
)
```

## Tools and references

**Workflow infrastructure**

- Snakemake ŌĆö M├Člder F. et al. (2021). *F1000Research* 10:33. [doi:10.12688/f1000research.29032.2](https://doi.org/10.12688/f1000research.29032.2)
- nf-core/rnaseq ŌĆö Ewels P.A. et al. (2020). *Nat Biotechnol.* 38, 276ŌĆō278. [doi:10.1038/s41587-020-0439-x](https://doi.org/10.1038/s41587-020-0439-x)
- Quarto ŌĆö <https://quarto.org>

**Quantification, counts, and QC**

- Salmon ŌĆö Patro R. et al. (2017). *Nat Methods* 14, 417ŌĆō419. [doi:10.1038/nmeth.4197](https://doi.org/10.1038/nmeth.4197)
- tximport ŌĆö Soneson C., Love M.I., Robinson M.D. (2015). *F1000Research* 4:1521. [doi:10.12688/f1000research.7563.2](https://doi.org/10.12688/f1000research.7563.2)
- MultiQC ŌĆö Ewels P. et al. (2016). *Bioinformatics* 32(19), 3047ŌĆō3048. [doi:10.1093/bioinformatics/btw354](https://doi.org/10.1093/bioinformatics/btw354)

**Differential expression**

- DESeq2 ŌĆö Love M.I., Huber W., Anders S. (2014). *Genome Biol.* 15, 550. [doi:10.1186/s13059-014-0550-8](https://doi.org/10.1186/s13059-014-0550-8)
- apeglm ŌĆö Zhu A., Ibrahim J.G., Love M.I. (2019). *Bioinformatics* 35(12), 2084ŌĆō2092. [doi:10.1093/bioinformatics/bty895](https://doi.org/10.1093/bioinformatics/bty895)

**Gene-set analysis**

- GSEA (method) ŌĆö Subramanian A. et al. (2005). *PNAS* 102(43), 15545ŌĆō15550. [doi:10.1073/pnas.0506580102](https://doi.org/10.1073/pnas.0506580102)
- fgsea ŌĆö Korotkevich G. et al. (2021). *bioRxiv.* [doi:10.1101/060012](https://doi.org/10.1101/060012)
- clusterProfiler 4.0 ŌĆö Wu T. et al. (2021). *The Innovation* 2(3), 100141. [doi:10.1016/j.xinn.2021.100141](https://doi.org/10.1016/j.xinn.2021.100141)
- MSigDB / Hallmark ŌĆö Liberzon A. et al. (2015). *Cell Systems* 1(6), 417ŌĆō425. [doi:10.1016/j.cels.2015.12.004](https://doi.org/10.1016/j.cels.2015.12.004)

**Regulatory and pathway activity inference**

- decoupleR / decoupler-py ŌĆö Badia-i-Mompel P. et al. (2022). *Bioinformatics Advances* 2(1), vbac016. [doi:10.1093/bioadv/vbac016](https://doi.org/10.1093/bioadv/vbac016)
- CollecTRI ŌĆö M├╝ller-Dott S. et al. (2023). *Nucleic Acids Research* gkad841. [doi:10.1093/nar/gkad841](https://doi.org/10.1093/nar/gkad841)
- PROGENy ŌĆö Schubert M. et al. (2018). *Nat Commun* 9, 20. [doi:10.1038/s41467-017-02391-6](https://doi.org/10.1038/s41467-017-02391-6)

**cMap / connectivity**

- L1000 Connectivity Map ŌĆö Subramanian A. et al. (2017). *Cell* 171(6), 1437ŌĆō1452. [doi:10.1016/j.cell.2017.10.049](https://doi.org/10.1016/j.cell.2017.10.049)
- L2S2 ŌĆö L1000 signature search (Ma'ayan Lab). <https://l2s2.maayanlab.cloud>

## Session info

```{r audit-sessioninfo}
# Keep only reproducibility-relevant fields: R version, platform, OS,
# attached packages + versions, and loaded-via-namespace packages.
# Drop: BLAS/LAPACK install paths, locale, time zone, RNG kind.
si <- utils::capture.output(sessionInfo())

drop_pat <- paste0(
  "^(Matrix products:",
  "|BLAS(/LAPACK)?:|LAPACK:",
  "|locale:",
  "|time zone:",
  "|tzcode source:",
  "|Random number generation:",
  "|\\s+\\[\\s*\\d+\\]\\s+LC_",
  "|\\s+(RNG|Normal|Sample):)"
)
si <- si[!grepl(drop_pat, si)]

# Collapse runs of consecutive blank lines left behind by removals.
prev_blank <- FALSE
keep <- logical(length(si))
for (i in seq_along(si)) {
  is_blank <- !nzchar(trimws(si[i]))
  keep[i] <- !(is_blank && prev_blank)
  prev_blank <- is_blank
}
cat(si[keep], sep = "\n")
```
