# QC

::: lang-en
Per-sample QC metrics from MultiQC. Sample quality (degradation, contamination, library-prep deviations).
:::

::: lang-ko
MultiQC 출력에서 집계한 샘플별 QC 지표. 샘플 품질(분해, 오염, 라이브러리 이상) 평가.
:::

```{r qc-load}
qc_path <- rp("results", "qc", "qc_summary.tsv")
qc <- safe_read(qc_path, sep = "\t")
```

```{r qc-table}
if (is.null(qc) || nrow(qc) == 0) {
  no_results("QC summary table not available.")
} else {
  qc_show <- qc
  numeric_cols <- c("mapping_rate", "uniquely_mapped_pct",
                    "rrna_pct", "duplication", "dupradar_slope",
                    "exonic_pct", "intronic_pct", "intergenic_pct",
                    "gene_body_5_3_bias", "insert_size_median",
                    "gc_content_pct")
  for (col in intersect(numeric_cols, names(qc_show))) {
    if (is.numeric(qc_show[[col]])) {
      qc_show[[col]] <- signif(qc_show[[col]], 3)
    }
  }
  knitr::kable(qc_show,
               row.names = FALSE,
               booktabs  = TRUE,
               longtable = TRUE,
               caption   = "Per-sample QC metrics")
}
```

## Library size

```{r qc-libsize, fig.width=7, fig.height=3.5}
if (is.null(qc) || nrow(qc) == 0 || !"assigned_reads" %in% names(qc)) {
  no_results("Per-sample assigned-read totals not available.")
} else {
  df <- qc |>
    dplyr::mutate(
      sample    = factor(sample, levels = sample),
      condition = as.character(condition)
    )
  p <- ggplot2::ggplot(df, ggplot2::aes(
        x = sample, y = assigned_reads, fill = condition
      )) +
    ggplot2::geom_col() +
    ggplot2::scale_y_continuous(labels = scales::comma) +
    ggplot2::labs(x = NULL, y = "Assigned reads (sum of counts)") +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))
  print(p)
}
```

## Mapping, contamination, complexity

```{r qc-rates, fig.width=8, fig.height=5}
if (is.null(qc) || nrow(qc) == 0) {
  no_results("QC rate metrics not available.")
} else {
  rate_cols <- intersect(
    c("mapping_rate", "uniquely_mapped_pct", "rrna_pct",
      "duplication", "dupradar_slope", "exonic_pct"),
    names(qc)
  )
  rate_cols <- rate_cols[vapply(rate_cols, function(c) any(!is.na(qc[[c]])), logical(1))]
  if (length(rate_cols) == 0) {
    no_results("All rate metrics are NA.")
  } else {
    df <- qc |>
      dplyr::select(sample, condition, dplyr::all_of(rate_cols)) |>
      tidyr::pivot_longer(dplyr::all_of(rate_cols),
                          names_to = "metric", values_to = "value") |>
      dplyr::mutate(sample = factor(sample, levels = unique(sample)))
    p <- ggplot2::ggplot(df, ggplot2::aes(x = sample, y = value, fill = condition)) +
      ggplot2::geom_col() +
      ggplot2::facet_wrap(~ metric, scales = "free_y") +
      ggplot2::labs(x = NULL, y = NULL) +
      ggplot2::theme_minimal(base_size = 11) +
      ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))
    print(p)
  }
}
```

## Sample handling indicators

::: lang-en
Cohort-relative outliers in these metrics indicate sample-specific preparation issues.

-   `gene_body_5_3_bias` — RNA integrity indicator. \~1.0 = normal, \<0.5 = 3' bias from transcript truncation.
-   `intronic_pct`, `intergenic_pct` — excess pre-mRNA or genomic DNA carryover.
-   `insert_size_median` — fragmentation indicator.
-   `gc_content_pct` — foreign-organism contamination or adapter dimers.
:::

::: lang-ko
Cohort 내 한 샘플이 다음 지표에서 outlier로 나타나면 해당 샘플의 처리 단계를 점검.

-   `gene_body_5_3_bias` — RNA 무결성 지표, 1.0 부근은 정상, 0.5 미만은 transcript truncation에 의한 3' bias.
-   `intronic_pct`, `intergenic_pct` — pre-mRNA 과다 또는 genomic DNA carryover.
-   `insert_size_median` — fragmentation 지표.
-   `gc_content_pct` — 외래 종 오염 또는 adapter dimer.
:::

```{r qc-handling, fig.width=8, fig.height=5}
if (is.null(qc) || nrow(qc) == 0) {
  no_results("Handling-indicator metrics not available.")
} else {
  cols <- intersect(
    c("gene_body_5_3_bias", "intronic_pct", "intergenic_pct",
      "insert_size_median", "gc_content_pct"),
    names(qc)
  )
  cols <- cols[vapply(cols, function(c) any(!is.na(qc[[c]])), logical(1))]
  if (length(cols) == 0) {
    no_results("Handling-indicator metrics all NA — confirm MultiQC modules (RSeQC geneBody_coverage / read_distribution, samtools stats, FastQC) are present.")
  } else {
    df <- qc |>
      dplyr::select(sample, condition, dplyr::all_of(cols)) |>
      tidyr::pivot_longer(dplyr::all_of(cols),
                          names_to = "metric", values_to = "value") |>
      dplyr::mutate(sample = factor(sample, levels = unique(sample)))
    p <- ggplot2::ggplot(df, ggplot2::aes(x = sample, y = value, fill = condition)) +
      ggplot2::geom_col() +
      ggplot2::facet_wrap(~ metric, scales = "free_y") +
      ggplot2::labs(x = NULL, y = NULL) +
      ggplot2::theme_minimal(base_size = 11) +
      ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1))
    print(p)
  }
}
```

```{r qc-strand-check, results='asis'}
if (!is.null(qc) && "strandedness" %in% names(qc) && any(!is.na(qc$strandedness))) {
  calls <- unique(stats::na.omit(qc$strandedness))
  if (length(calls) == 1) {
    cat(sprintf(
      "_Inferred strandedness (RSeQC infer_experiment): **%s** for all samples._\n",
      calls
    ))
  } else {
    tab <- table(qc$strandedness)
    mixed <- paste(sprintf("%s (n=%d)", names(tab), as.integer(tab)),
                   collapse = ", ")
    cat(sprintf(
      "_Inferred strandedness varies across samples: %s. Confirm library-preparation records before counting._\n",
      mixed
    ))
  }
}
```